### 2010-07-01 paper/IIWAS2010/content/abstract.tex
IIWAS 2010 submission: Initial draft
latest commit before added joirdan altered diagram

\begin{abstract}
The Morpheus question answering system uses deep web search to answer
user queries. Queries are represented as OWL ontologies that reference
categories within specific ontological realms.
The system answers questions by using methods identified in prior
successful searches answering similar queries.
Stored methods are ranked based on their ontological similarity to the
question being answered.
The similarity measure depends on finding the distance between
ontological categories associated with their search terms.
The DBpedia and Wikipedia provide information we use to identify the likely
categories associated with those terms.
Finally, we replay appropriately re-parameterized relevant prior searches
to construct possible answers.
The paper describes this entire process with emphasis on the matching of
user queries to stored answering methods.
\end{abstract}

>>>>

\begin{abstract}

The Morpheus question answering system uses deep web search to answer user queries. Queries are represented by a semi-structured format that contains query terms and referenced classes within a specific ontology.  Morpheus answers questions by using methods from prior successful searches.  The system ranks stored methods based on a similarity quasi-metric defined on assigned classes of queries. Similarity depends on the class heterarchy in an ontology and its associated text corpora. Finally, Morpheus revisits the prior search pathways of the stored searches to construct possible answers. The realm-based ontologies are created using Wikipedia pages, associated categories, and the synset heterarchy of WordNet. This paper describes the entire process with emphasis on the matching of user queries to stored answering methods.

\end{abstract}

### 2010-07-01 paper/IIWAS2010/content/introduction.tex
small intro change
latest commit before added joirdan altered diagram

When traveling though a jungle to a destination, it is easy to get
lost.  The first person to go somewhere may make a number of mistakes
in trying to find the best path to their destination. Those
who come later find it easier to reach the destination if a
well-marked trail has been created. Olsen and Malizia describe this
idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
a user's discovery experience as a unique entity, one can exploit the fact that a similar search may have already been
performed.  In one study, almost 40 percent of all queries
were repetitions of previous queries\cite{1277770}. Thus, reuse of prior searches is one way to optimize the search
process.  Morpheus is a question answering system motivated by reuse of prior
web search pathways to yield an answer to a user query. Morpheus follows path-finders to their destinations and not only marks the
trail, but also provides a taxi service to take followers to similar
destinations.

There are two distinct Morpheus user roles. A
\textit{path finder} enters queries in the Morpheus web interface and
searches for an answer to the query using an instrumented web browser. 
This web tracking tool stores the query
and necessary information to revisit the pathways to the page where the guide 
found the answer. A \textit{path follower} uses the Morpheus system much like a regular search engine with a natural language interface. The path follower enters a question in a text box and receives a guided path to the answer. The system exploits previously found paths to provide an answer.

Morpheus represents user-query details in a semi-structured query (SSQ). It includes a user query in natural-language format, relevant terms for the query, and place holders for the term \textit{categories}. A \textit{category} represents a
topic or class to which a term belongs. For example, the term \textit{tire} can be classified into the category \textit{Automotive Part}.

Morpheus assumes the term categories are classes of a
\textit{consistent} realm-based ontology, that is, one having a singly rooted heterachy whose
subclass/superclass relations have meaningful semantic interpretations. When a path-follower enters a query, Morpheus ranks SSQs in the store based on category similarity. Suppose a
regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In
this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars
and a predecessor of \textit{automobile models} is important, because this will
help us grouping stored queries.

This paper discusses related question answering and ontology generation systems in section \ref{sec:relatedwork}. Section \ref{sec:systemarch} explains the Morpheus system and its implementation. Section \ref{sec:results}, we describe current results and their
interpretation. We conclude by describing the global impacts
of our approaches in QA systems.

>>>>

When traveling though a jungle to a destination, it is easy to get lost.  The first person to journey somewhere may make a number of mistakes when trying to find the best path to their destination. Those who come later find it easier to reach the destination if a well-marked trail has been created. Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating a user's discovery experience as a unique entity, one can exploit the fact that a similar search may have already been performed.  In one study, almost 40 percent of all queries were repetitions of previous queries\cite{1277770}. Thus, reuse of prior searches is one way to optimize the search
process.  Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query. Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar
destinations.

There are two distinct Morpheus user roles. A
\textit{path-finder} enters queries in the Morpheus web interface and
searches for an answer to the query using an instrumented web browser. 
This web tracking tool stores the query
and necessary information to revisit the pathways to the page where the path-finder 
found the answer. A \textit{path-follower} uses the Morpheus system much like a regular search engine with a natural language interface. The path-follower enters a question in a text box and receives a guided path to the answer. The system exploits previously found paths to provide an answer.

Morpheus represents user-query details in a semi-structured query (SSQ). It assumes the terms belong to classes of a \textit{consistent} realm-based ontology, that is, one having a singly rooted heterarchy whose subclass/superclass relations have meaningful semantic interpretations. When a path-follower enters a query, Morpheus ranks SSQs in the store based on class similarity. Suppose a regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In this query the classes associated with terms, e.g. \emph{Manufacturer} with \emph{Toyota}, helps us identify similar queries.

This paper discusses related question answering and ontology generation systems in section \ref{sec:relatedwork}. Section \ref{sec:systemarch} explains the Morpheus system and its implementation. In Section \ref{sec:results} we describe the current results of our approach.  Finally, we conclude with future goals for the system.
